Assessing United States county-level exposure for tropical cyclone impact research

### 2020-09-11 ehp_revision/response_to_reviewers.Rmd

Thank you for this suggestion. We have changed the wording in this sentence:

> **Text in revised manuscript (relevant change in bold):**
"In many cases, these studies analyze multi-year, multi-community data, allowing
them to estimate average associations over many disasters and to explore how a
disaster's characteristics, or the characteristics of the **affected
communities**, modify associated health risks (e.g., Anderson and Bell 2010; Son
et al. 2012; Liu et al. 2017)."

We also used the word "Hits per county per decade" in the legend for Figure 5 in
the main text (reproduced in this response document as Figure \@ref(fig:fig5))
and Figure S3 of the Supplemental Material. We have revised the wording in these
figures to "Exposures per county per decade".

```{r fig5, fig.cap="Reproduction of Figure 5 from the original manuscript (left) and revised version in the resubmitted manuscript (right). In the revised version, the figure legend was changed from '\\textbf{Hits} per county per decade' to '\\textbf{Exposures} per county per decade' (bold used to highlight change). Figure caption in the revised manuscript: \\textit{Figure caption.}", fig.show = "hold", out.width="40%", fig.align = "center"}
include_graphics("../figures/averageexposureonly.pdf")
include_graphics("figures/averageexposureonly.pdf")
```

### 2020-09-13 ehp_revision/response_to_reviewers.Rmd

---
title: "Response to reviewers' comments for *\"Assessing United States county-level exposure for research on tropical cyclones and human health\"*"
output: bookdown::pdf_document2
toc: false
bibliography: writing/hurr_exposure.bib
header-includes:
- \usepackage{xcolor}
- \usepackage{framed}
- \usepackage{bm}
- \usepackage{subcaption}
- \usepackage{gensymb}
- \renewcommand\familydefault{\sfdefault}
- \usepackage{sansmath}
- \usepackage{bm}
- \usepackage{soul}
- \sansmath
- \usepackage{booktabs}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{pdflscape}
- \usepackage{float}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{fullpage}
- \usepackage{pdflscape}
- \usepackage{tcolorbox}
- \tcbuselibrary{skins,breakable}
- \usepackage{amsmath}
- \usepackage{xtab}
- \usepackage{rotating}
- \allowdisplaybreaks
- \usepackage[nomarkers]{endfloat}
- \pagenumbering{gobble}
- \newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
- \usepackage{longtable}
- \DeclareDelayedFloatFlavor{longtable}{table}
---

@@

\begin{shaded}
\textbf{Reviewer 1 (R1) Comment 1:}
I very much appreciate the rationale for authors' decision to focus at the
county level, especially given the available health-related data. But, since
tropical cyclones don't necessarily have consistent impacts across an entire
county, I think the limitations of this decision are worthy of further
discussion in the discussion section.
\end{shaded}

**Response:**

This is an excellent point. We have added text in the Limitations section of the
Discussion on the potential limitations of using aggregated, county-level
exposure data in a research study:

> **Text added to Discussion (added text in bold):** 
"Second, these data are aggregated to the county level. **This spatial scale
allows for easy integration with health outcome data aggregated at the county
level. Such data is often used for disaster epidemiology, as aggregated data may
be easier to access than individual-level data, especially at a scale that
covers many locations and years and so allows higher statistical power and
includes a broader range of exposure levels [@wakefield2008overcoming].**

> "**Such ecological exposure assessment, however, sets a common exposure level
throughout the county, ignoring within-county variability, even though such
variability exists. For some hazards, this within-county variation could be
stark. For example, tornadoes cause very localized damage, directly along the
tornado's path---a tornado can destroy homes on one side of a street while
leaving those on the opposite side untouched. Levels of other hazards, like
storm-associated winds and rain, will also vary within a county, but typically
with smoother variation. In particular, it will be unlikely that a county will
have one area that is exposed to extremes of these hazards while other parts of
the county are completely unexposed, as both the wind fields and rain fields of
tropical cyclones tend to be large in comparison to the size of a county.**

> "**Aggregated data can be used to infer contextual-level associations---for
example, the association between county-level exposure to a storm hazard and
county-wide rates of a health outcome. However, ecological data is also
sometimes used to infer individual-level associations (e.g., the association
between personal exposure to a storm hazard and personal risk of  experiencing
the health outcome). Individual-level inference from ecological/aggregated data
is susceptible to ecological bias [@greenland1994invited; @portnov2007ecological;
@idrovo2011three]. Researchers who use the data provided here for ecological
studies---with the aim of making individual-level inferences---should be aware
of this potential and could explore approaches for minimizing risk of ecological
bias (e.g., @wakefield2008overcoming).**"

@@

\begin{shaded}
\textbf{R1 Comment 2:}
Are there opportunities to expand this approach internationally? Some decisions
(e.g., county-level) data may restrict cross-country comparisons. Can the
authors discuss this? 
\end{shaded}

**Response:**

While there would be some limitations in comparisons based on differences in the
scale of county-equivalents, many countries affected by tropical cyclones do
have geopolitical areas that are fairly comparable to US counties, like
municipalities in Mexico, districts in India. There would be a few challenges,
however, in extending the exposure dataset for the hazards that we present in
this paper. We have added text to the paper's Discussion on opportunities and
barriers to expanding this approach internationally:

> Text added to the Discussion (added text in bold): 
"**This dataset is limited to the contiguous US, and while expansion to global
coverage would be useful and feasible, there would be some challenges. For
precipitation data, the re-analysis product used here (NLDAS-2) only covers the
contiguous US, although other re-analysis products, as well as other types of
precipitation datasets, have global coverage [@sun2018review]. The wind data are
generated based on a model that is currently US-focused [@stormwindmodel], but
could be extended to other areas, although this would require adding new
land/sea masks within the associated software, as well as accounting for
differences across storm basins in wind averaging periods
[@harper2010guidelines] and in the direction of cyclonic winds in the Northern
versus Southern Hemisphere. Further, since the core of the wind model was
developed based on data from Atlantic-basin storms [@willoughby2006parametric],
an extension to other areas should include separate validation and calibration
to ensure it performs appropriately in those settings. Alternatively, other wind
field modeling software is available that provides a global coverage, like
Geoscience Australia's Tropical Cyclone Risk Model
(http://geoscienceaustralia.github.io/tcrm/). For tornado and flood events, the
data described in this paper drew on a US-focused storm events database, and so
international extension of data on these hazards would require access to similar
databases covering other countries. Finally, the relevant geopolitical
boundaries to use for aggregation would vary by country (e.g., municipalities in
Mexico, districts in India).**"

@@

However, there are some limitations to the FEMA disaster declarations in terms
of using them as a proxy for the amount of damage a storm caused in a county.
FEMA's disaster declarations are issued to provide assistance, based on damage
assessment, to individuals or the entire public in certain locations where
catastrophes overwhelm the state or local government [@mccarthy2014fema], and
any use of them for exposure assessment is secondary. Due to the political
nature of disaster declaration process, these declarations are often subject to
many political and economic factors [@mccarthy2014fema; @logue1981research].
Given the political and economic nature of these declarations, there is likely
variation across time and geography in the likelihood of a given exposure
resulting in a disaster declaration. This would be particularly worrisome for a
study that seeks to explore risk across multiple years and affected communities.

Other sources of data may therefore be better suited to use as a marker of
damage to assess that pathway of indirect health impacts from a tropical
cyclone. For example, data on storm impacts, including property damage or
insurance claims data, are sometimes available through storm databases or
publications (e.g., NOAA's Storm Events data, tropical cyclone reports published
in the *Monthly Weather Review*). While such data could potentially be used to
create an exposure metric, tropical storm damage data requires some
normalization, to incorporate both changes in dollar value over time and also
changes in development in at-risk areas, to be comparable over extended time
periods [@pielke1998].

We have added text discussing this point to the Discussion:

> **Text in revised manuscript (added text in bold):**
"**The dataset we present focuses on the physical hazards of a tropical cyclone.
However, health impacts will often come through indirect pathways, including
through damage to property and infrastructure. In future work, it would be
useful to expand this dataset to add data related to these pathways, to allow
research exploring the role of indirect pathways from tropical cyclone phyiscal
hazards to health risk. This expansion could include adding data on normalized
storm-associated damages, or proxy measurements of such damages, from sources
like the US NOAA's Storm Events database and the US Federal Emergency Management
Agency's county-level disaster declarations.**"

@@

This is great, because it might otherwise be difficult to try to maintain copies
of the dataset in different repositories (i.e., one copy as an R package and
another as a DesignSafe dataset), and there could be confusion about things like
the equivalence of the two copies. R packages are citable through a standard
format that gives the R package version, while data publicly shared on
DesignSafe is assigned a digital object identifiers (DOI)
[@rathje2017designsafe], and so different citations would be used for the same
dataset depending on how the user accessed it. If updates of one copy were not
immediately updated for the other copy, the copies could get out of sync, and
maintaining two synced copies would add would add an extra layer of work with
each update to the R package (we have been updating several hazards as new data
becomes available). DesignSafe's interface with R avoids this problem by
allowing its users direct access to our package and its data through that path,
as it allows for a single, citable, licensed version of the data stored and
shared from a single location, with no question of syncing separate versions of
the data or clarifying licensing and citation practices across two storage
locations.

We have added a note in the manuscript to let readers know that, because the
data is shared through an R package, and because DesignSafe's Discovery
Workspace allows users to work in R, the data can be fully accessed and used for
those working on the DesignSafe platform by using the same code in a DesignSafe
Jupyter notebook that would otherwise be used on a local computer.

> **Text added to the Methods of the revised manuscript (added text in bold):**
"We have posted most study data as an open-source R package (Anderson et al.
2020). **By sharing this data as an R package, it is also accessible through
cloud-based computing platforms that incorporate Jupyter notebooks, including
the National Science Foundations's DesignSafe platform for natural hazards
engineering research [@rathje2017designsafe].**"

@@

Second, in cases where it is clear that a mixture approach is necessary, these
results can help in understanding what challenges might arise in statistical
analysis. While one approach to including several hazards could be to create an
index of tropical cyclone exposure by taking a weighted sum of all hazards, for
most health outcomes it is unclear *a priori* what the weight for each hazard
should be in such an index, and so it will often be preferable to discover those
weights from the data by fitting a statistical model that includes each hazard
as an independent variable. In these cases, strong correlation (or agreement, in
the case of binary exposures) among separate independent variables can create
both numerical issues (e.g., variance inflation from multicollinearity) and
difficulties in interpretation (e.g., difficulty infering the role of specific
hazards and separating the influece of each). If an epidemiologist has a good
understanding of these patterns in their data, he or she can adopt methods that
address potential issues, including using matching-based study designs to create
a subset of storms to study in which separate hazards are well-distinguished
from each other, incorporation of dimension-reduction methods like principal
components analysis, or shrinkage techniques that allow for a small amount of
bias in estimation of associations in return for reducing problems from
collinearity (e.g., ridge regression) [@leal2012multicollinearity;
@schisterman2017collinearity].

The reviewer makes a good point that it is important for us to clarify our
motivation for measuring agreement between the hazard-based metrics, as well as
to show readers how our results from these measures can be used to help in
designing studies and planning statistical analysis for tropical cyclone
epidemiology. We have added text to the manuscript on these points:

> "Finally, we investigated how well exposure assessment agreed across these
metrics. **These results can help epidemiologists answer several key
questions as they interpret previous research and design new studies. For
example, if a single storm hazard has been used to measure exposure in an
epidemiological study, can the result be interpreted as an association with
tropical cyclone exposure in general, or should it be limited to represent an
association with that specific storm hazard? If a study investigates the
association between a single storm hazard and a health outcome, could this
estimate be confounded by other storm hazards? When planning a new study that
will incorporate several storm hazards, might there be variance inflation from
multicollinearity or difficulties in disentangling the roles of separate
hazards?**"

@@

\input{tables/precip_high_corr.tex}

In several cases, the correlation was much weaker when limiting analysis to
these severe rainfall events. For example, in Miami-Dade County, FL, the
Spearman correlation coefficient was 0.94 for all 64 tropical cyclones that came
near the county over the analysis period, while it was only 0.49 among the 18
storms with cumulative precipitation of 75 mm or more. There was a similar
reduction in Mobile County, AL. However, for some counties, the correlation
remained high (e.g., Harris County, TX; Orleans Parish, LA), although in all
cases there are small numbers of extreme precipitation events (5--20 across
these sample counties), and so there is likely substantial random variation in
these correlation estimates, since they are based on small numbers of 
observations.

We have added text to mention this point and to direct readers to the added
supplemental table:

> **Text in revised Results (relevant addition in bold):**
"The rainfall data are generally well-correlated with ground-based
observations, but may sometimes underestimate very high rainfall values (Figure
2). **Further, in some counties, the correlation was substantially lower when 
considering only tropical cyclones with cumulative local rainfall of 75 mm
or more (Supplemental Table 1)**."

> **Text in revised Discussion (relevant addition in bold):**
"The rainfall data are generally well-correlated with ground-based observations,
but may sometimes underestimate very high rainfall values (Figure 2), **and in
some counties the correlation was substantially lower when considering only
tropical cyclones with cumulative local rainfall of 75 mm or more (Supplemental
Table 1).**"

@@

\input{tables/tornado_misclass.tex}

We have added four new tables in the Supplemental Material, one for each of the
hazard-based metrics we considered. We have reproduced these tables in this
response document as Tables \@ref(tab:misclasswind)--\@ref(tab:misclassflood)
Each breaks down agreement and disagreement between the distance-based proxy
metric and that hazard-based metric within several storms in our study period.
These tables focus on storms with at least 250 counties exposed by at least one
of the metrics considered. These tables allow readers both to investigate
general patterns in disagreement and exposure misclassification across these
storms and also to see cases of unusual storms. For example, for most storms,
disagreement between the distance proxy metric and the wind-based metric
resulted mainly from mis-classification of counties as exposed based on distance
while they did not experience gale-force winds. However, there were a few
storms, like Hurricane Bertha in 1996, where the inverse was the case, and a
distance-based metric would have missed a large number of counties that
experienced gale-force winds from the storm (misclassified them as unexposed),
but not misclassified many counties as exposed when they in fact did not
experience winds at this level.

We have added a reference to these new tables in the main text of the manuscript:

> **Text in the revised manuscript (relevant addition in bold):** 
"We drew similar conclusions when we investigated all 46 tropical cyclones
between 1996 and 2011 (when data for all five metrics were available) for
which~100 or more counties were exposed based on at least one metric (Figure7;
**for the most extensive of these, storms for which 250 of more counties were
exposed based on at least one metric, Tables S3--S6 provide underlying numbers
comparing exposure assessments for the distance-based proxy to each hazard-based
metric**)."

> **Text in the revised manuscript (relevant addition in bold):**
"Based on our results, the use of a distance-based metric to assess exposure to
any of these hazards, or the use of measurements from one hazard as a proxy for
exposure to any of the other hazards considered, would often introduce exposure
misclassification **(Figure 7, Tables S3--S6)**."

@@

\begin{shaded}
\textbf{R3 Comment 6:}
Table 1: I suggest providing the rationale for picking the thresholds for
classifying continuous exposures into binary ones within the table. 
\end{shaded}

**Response:**

For all outcomes, there are various reasonable choices that can be picked for
the threshold in defining exposure. There is not room to go into these details
within Table 1, so instead we added a separate table to the Supplemental
Material that provides both some reasoning behind the thresholds selected in
this study and also other reasonable thresholds that could be considered.
This is Table S1 of the revised manuscript and has been reproduced as 
Table \@ref(tab:thresholds) at the end of this response document.

\begin{longtable}{lp{40em}}
\caption{Caption. These are provided for the three exposure metrics for which our database includes continuous data, and so a threshold is selected to determine binary exposure based on the metric. This table provides reasoning for the choice of threshold used in this paper as well as guidance on other thresholds that could be considered, depending on the hypothesized pathways for an epidemiological study.}
\label{tab:thresholds} \\
\hline
Metric & Threshold choice\\
\hline
Distance & In the manuscript, distance-based exposure was assessed if the storm track came within 100 km of county population mean center. This threshold for distance from the storm center has been used in prior research as a proxy for exposure to hazards from the storm \cite{grabich2015measuring}. Tropical cyclones vary dramatically in size: US tropical cyclones have been observed with radii to maximum winds as small as 20 km and as large as 200 km \cite{mallin2006, quiring2011variations}, and dangerous winds can extend beyond these maximum winds. One study \cite{czajkowski2011} assessed county-level risk and exposure based on a three-tiered definition, with primary counties being those closest to the storm track on either side, secondary counties being adjacent to primary counties, and tertiary counties adjacent to secondary counties. Such a definition resulted in an exposure defenition based on an average distance radius of 120 km on either side of the storm track \cite{czajkowski2011}. Other distance thresholds that could be considered include 60 km and 30 km, both of which have been used in previous research \cite{grabich2015measuring, grabich2015, currie2013}.\\
Rain & In the manuscript, rain-based exposure was assessed if the county had cumulative rainfall of $\ge75$ mm over the period from two days before to one day after the storm’s closest approach and the storm track came within 500 km of the county population mean center. This threshold... Other reasonable definitions could vary both the threshold of rainfall (in mm) and also the choice of days surrounding the storm to include when calculating the cumulative rainfall. Tropical cyclone precipitation arrives before the center of the storm \cite{zhou2017spatial}. A variety of definitions have been used to identify both extreme or heavy rain (whether associated with a tropical cyclone or not) and tropical cyclone--associated rain. Some definitions of extreme rain events are higher than the threshold we use here---for example, one paper defined extreme rain events as cases in which a gauge reported 125 mm or more of rain in 24 hours \cite{schumacher2006characteristics}. Studies have also used definitions that are relative to the norms for a given location (e.g., 24 hour rainfall totals over the 50-year return value for the location, which the part of the US east of the Rocky Mountains range from 3.5 in [89 mm] to 13 in [330 mm]). \cite{schumacher2006characteristics, schumacher2005organization, stevenson201410}. A study focused on the risks that result from extreme rainfall may therefore reasonably choose a higher threshold than the 75 mm threshold we use in this analysis. In defining precipitation associated with tropical cyclones, studies have used thresholds of 12.5 mm per day as a metric of regions of ``moderately heavy'' rainfall \cite{zhou2017spatial} and, as a lower threshold, a lower limit of 10 mm of total storm precipitation---in conjunction with proximity to the storm's center---in identifying tropical cyclone precipitation events at a location \cite{feldmann2019estimation}. \\
Wind & In the manuscript, wind-based exposure was assessed if modeled storm-associated peak sustained surface wind of $\ge34$ kts at the county’s population mean center. This threshold is being applied to local winds for each county, and it represents the threshold for gale-force winds on the Beaufort wind scale. This limit is used as the outer limit in measuring storm size through the US National Hurricane Center's wind radii for tropical cyclone forecasts \cite{cangialosi2016examination}. Other thresholds could be selected based on other points on the Beaufort scale---for example, $\ge48$ kts for capturing storm-force winds or $\ge64$ kts for capturing hurricane-force winds. As a note, hurricane-force winds will be rarely experienced for counties, as it will likely only be observed for very severe storms and even for those for counties near the storm's landfall. Many presentations of the Beaufort wind scale include descriptions of the conditions that winds in each category would produce both over land and at sea.\\
\hline
\end{longtable}

### 2020-09-13 ehp_revision/tables/thresholds_table.tex
Work some more on response
Continue work on revisions

\begin{table}

@@

\centering
\begin{tabular}{>{\bfseries\leavevmode\color{black}}l>{\raggedright\arraybackslash}p{40em}}
\toprule

@@

\midrule
Distance & In the manuscript, distance-based exposure was assessed if the storm track came within 100 km of county population mean center. This threshold for distance from the storm center has been used in prior research as a proxy for exposure to hazards from the storm \cite{grabich2015measuring}. Tropical cyclones vary dramatically in size: US tropical cyclones have been observed with radii to maximum winds as small as 20 km and as large as 200 km \cite{mallin2006, quiring2011variations}, and dangerous winds can extend beyond these maximum winds. One study \cite{czajkowski2011} assessed county-level risk and exposure based on a three-tiered definition, with primary counties being those closest to the storm track on either side, secondary counties being adjacent to primary counties, and tertiary counties adjacent to secondary counties. Such a definition resulted in an exposure defenition based on an average distance radius of 120 km on either side of the storm track \cite{czajkowski2011}. Other distance thresholds that could be considered include 60 km and 30 km, both of which have been used in previous research \cite{grabich2015measuring, grabich2015, currie2013}.\\
Rain & In the manuscript, rain-based exposure was assessed if the county had cumulative rainfall of $\ge75$ mm over the period from two days before to one day after the storm’s closest approach and the storm track came within 500 km of the county population mean center. This threshold... Other reasonable definitions could vary both the threshold of rainfall (in mm) and also the choice of days surrounding the storm to include when calculating the cumulative rainfall. Tropical cyclone precipitation arrives before the center of the storm \cite{zhou2017spatial}. A variety of definitions have been used to identify both extreme or heavy rain (whether associated with a tropical cyclone or not) and tropical cyclone--associated rain. Some definitions of extreme rain events are higher than the threshold we use here---for example, one paper defined extreme rain events as cases in which a gauge reported 125 mm or more of rain in 24 hours \cite{schumacher2006characteristics}. Studies have also used definitions that are relative to the norms for a given location (e.g., 24 hour rainfall totals over the 50-year return value for the location, which the part of the US east of the Rocky Mountains range from 3.5 in [89 mm] to 13 in [330 mm]). \cite{schumacher2006characteristics, schumacher2005organization, stevenson201410}. A study focused on the risks that result from extreme rainfall may therefore reasonably choose a higher threshold than the 75 mm threshold we use in this analysis. In defining precipitation associated with tropical cyclones, studies have used thresholds of 12.5 mm per day as a metric of regions of ``moderately heavy'' rainfall \cite{zhou2017spatial} and, as a lower threshold, a lower limit of 10 mm of total storm precipitation---in conjunction with proximity to the storm's center---in identifying tropical cyclone precipitation events at a location \cite{feldmann2019estimation}. \\
Wind & In the manuscript, wind-based exposure was assessed if modeled storm-associated peak sustained surface wind of $\ge34$ kts at the county’s population mean center. This threshold is being applied to local winds for each county, and it represents the threshold for gale-force winds on the Beaufort wind scale. This limit is used as the outer limit in measuring storm size through the US National Hurricane Center's wind radii for tropical cyclone forecasts \cite{cangialosi2016examination}. Other thresholds could be selected based on other points on the Beaufort scale---for example, $\ge48$ kts for capturing storm-force winds or $\ge64$ kts for capturing hurricane-force winds. As a note, hurricane-force winds will be rarely experienced for counties, as it will likely only be observed for very severe storms and even for those for counties near the storm's landfall. Many presentations of the Beaufort wind scale include descriptions of the conditions that winds in each category would produce both over land and at sea.\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{longtable}{lp{40em}}

@@

\label{tab:thresholds} \\
\hline

@@

\hline
Distance & In the manuscript, distance-based exposure was assessed if the storm track came within 100 km of county population mean center. This threshold for distance from the storm center has been used in prior research as a proxy for exposure to hazards from the storm \parencite{grabich2015measuring}. Tropical cyclones vary dramatically in size: US tropical cyclones have been observed with radii to maximum winds as small as 20 km and as large as 200 km \parencite{mallin2006, quiring2011variations}, and dangerous winds can extend beyond these maximum winds. One study \parencite{czajkowski2011} assessed county-level risk and exposure based on a three-tiered definition, with primary counties being those closest to the storm track on either side, secondary counties being adjacent to primary counties, and tertiary counties adjacent to secondary counties. Such a definition resulted in an exposure defenition based on an average distance radius of 120 km on either side of the storm track \parencite{czajkowski2011}. Other distance thresholds that could be considered include 60 km and 30 km, both of which have been used in previous research \parencite{grabich2015measuring, grabich2015, currie2013}.\\
Rain & In the manuscript, rain-based exposure was assessed if the county had cumulative rainfall of $\ge75$ mm over the period from two days before to one day after the storm’s closest approach and the storm track came within 500 km of the county population mean center. This threshold... Other reasonable definitions could vary both the threshold of rainfall (in mm) and also the choice of days surrounding the storm to include when calculating the cumulative rainfall. Tropical cyclone precipitation arrives before the center of the storm \parencite{zhou2017spatial}. A variety of definitions have been used to identify both extreme or heavy rain (whether associated with a tropical cyclone or not) and tropical cyclone--associated rain. Some definitions of extreme rain events are higher than the threshold we use here---for example, one paper defined extreme rain events as cases in which a gauge reported 125 mm or more of rain in 24 hours \parencite{schumacher2006characteristics}. Studies have also used definitions that are relative to the norms for a given location (e.g., 24 hour rainfall totals over the 50-year return value for the location, which the part of the US east of the Rocky Mountains range from 3.5 in [89 mm] to 13 in [330 mm]). \parencite{schumacher2006characteristics, schumacher2005organization, stevenson201410}. A study focused on the risks that result from extreme rainfall may therefore reasonably choose a higher threshold than the 75 mm threshold we use in this analysis. In defining precipitation associated with tropical cyclones, studies have used thresholds of 12.5 mm per day as a metric of regions of ``moderately heavy'' rainfall \parencite{zhou2017spatial} and, as a lower threshold, a lower limit of 10 mm of total storm precipitation---in conjunction with proximity to the storm's center---in identifying tropical cyclone precipitation events at a location \parencite{feldmann2019estimation}. \\
Wind & In the manuscript, wind-based exposure was assessed if modeled storm-associated peak sustained surface wind of $\ge34$ kts at the county’s population mean center. This threshold is being applied to local winds for each county, and it represents the threshold for gale-force winds on the Beaufort wind scale. This limit is used as the outer limit in measuring storm size through the US National Hurricane Center's wind radii for tropical cyclone forecasts \parencite{cangialosi2016examination}. Other thresholds could be selected based on other points on the Beaufort scale---for example, $\ge48$ kts for capturing storm-force winds or $\ge64$ kts for capturing hurricane-force winds. As a note, hurricane-force winds will be rarely experienced for counties, as it will likely only be observed for very severe storms and even for those for counties near the storm's landfall. Many presentations of the Beaufort wind scale include descriptions of the conditions that winds in each category would produce both over land and at sea.\\
\hline
\end{longtable}
